Flaring star-planet interactions in star-planet systems in Kepler and TESS

### 2023-05-08 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}[t]
    \script{paper_spin_orbit_commensurability.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PAPER_spin_orbit_commensurable.png}
        \caption{
           \textbf{Top panel}: Same as the bottom left panel in Fig.~\ref{fig:adtest_bp}, but color coded as below. \textbf{Bottom panel:} Spin-orbit commensurability compared to flaring star-planet interaction signal. The lower the p-value of the AD test, the stronger the interaction signal. Lower relative difference between the measured spin-orbit ratio and the integer ratio closest to it indicates a tighter spin-orbit commensurability. We include only ratios of integers $<10$. \textbf{Black diamonds:} All systems with p-values lower than that of K2-25, and expected power of interaction equal or higher than TOI-540's, the active 'SPI on' branch~(see top left panel in Fig.~\ref{fig:adtest_bp}). \textbf{Red crosses:} The complementary 'SPI off' branch includes all systems with expected power of interaction above that of TOI-540, but with p-values below that of K2-25. \textbf{Blue circles:} The remaining systems include all with expected power of interaction below that of TOI-540. Among the systems with high expected power, those with higher interaction signal ('SPI on') show closer spin-orbit commensurability than those on the inactive 'SPI off' branch.
        }
        \label{fig:spinorbit}
    \end{centering}
\end{figure}

@@

Among the systems, HIP 67522 appears with tentative signs of both tidal and magnetic interaction (measured and expected in the different scenarios). KOI-12, which lacks signal with $P_{orb}$ despite high expected power of magnetic interaction, shows more consistency between expected and measured tidal interaction. This could be interpreted as KOI-12 b orbiting outside the ALfv\'en radius, unable to interact magnetically, but tidally. We note that KOI may be evolving off the main sequence, so that the tidal interaction estimates might not be accurate for this star. Finally, Kepler-42 is neither expected to interact magnetically, nor did it show any deviation from random flare timing in phase with $P_{orb}$. However, since it is the system with the shortest planetary orbit in our sample, it is both expected to and does show marginal signal of tidal interaction. Kepler-42 is very similar to TOI-540, which also is a small M dwarf with a likely terrestrial planet in a very short orbit. The key difference may be that Kepler-42 is rotating at about 70 days, and therefore expected to have a relatively weak magnetic field, whereas TOI-540 is a young star with a rotation period $<1\,$d. TOI-540 is expected to have lower tidal interaction strength than Kepler-42 due to TOI-540 b's wider orbit, and also shows a weaker tidal SPI signal in all three scenarios.

>>>>

\begin{figure}[t]
    \script{paper_spin_orbit_commensurability.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PAPER_spin_orbit_commensurable_p_spi_sb_bp1_norm.png}
        \caption{
           \textbf{Top panel}: Same as the bottom left panel in Fig.~\ref{fig:adtest_bp}, but color coded as below. \textbf{Bottom panel:} Spin-orbit commensurability compared to flaring star-planet interaction signal. The lower the p-value of the AD test, the stronger the interaction signal. Lower relative difference between the measured spin-orbit ratio and the integer ratio closest to it indicates a tighter spin-orbit commensurability. We include only ratios of integers $<10$. \textbf{Black diamonds:} All systems with p-values lower than that of K2-25, and expected power of interaction equal or higher than TOI-540's, the active 'SPI on' branch~(see top left panel in Fig.~\ref{fig:adtest_bp}). \textbf{Red crosses:} The complementary 'SPI off' branch includes all systems with expected power of interaction above that of TOI-540, but with p-values below that of K2-25. \textbf{Blue circles:} The remaining systems include all with expected power of interaction below that of TOI-540. Among the systems with high expected power, those with higher interaction signal ('SPI on') show closer spin-orbit commensurability than those on the inactive 'SPI off' branch.
        }
        \label{fig:spinorbit}
    \end{centering}
\end{figure}

@@

Among the systems, HIP 67522 appears with tentative signs of both tidal and magnetic interaction (measured and expected in the different scenarios). KOI-12, which lacks signal with $P_{orb}$ despite high expected power of magnetic interaction, shows elevated expected and measured tidal interaction. This could be interpreted as KOI-12 b orbiting outside the Alfv\'en radius, unable to interact magnetically, but tidally. We note that KOI may be evolving off the main sequence, so that the tidal interaction estimates might not be accurate for this star. Finally, Kepler-42 is neither expected to interact magnetically, nor did it show any deviation from random flare timing in phase with $P_{orb}$. However, since it is the system with the shortest planetary orbit in our sample, it is both expected to and does show marginal signal of tidal interaction. Kepler-42 is very similar to TOI-540, which also is a small M dwarf with a likely terrestrial planet in a very short orbit. The key difference may be that Kepler-42 is rotating at about 70 days, and therefore expected to have a relatively weak magnetic field, whereas TOI-540 is a young star with a rotation period $<1\,$d. TOI-540 is expected to have lower tidal interaction strength than Kepler-42 due to TOI-540 b's wider orbit, and also shows a weaker tidal SPI signal in all three scenarios.
